---
title: "01-assignment_<Crutchfield>"
author: "Russell Crutchfield"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1. A sentence that says “Hello, World”
print("Hello, World")

```{r}
## Clear environment
rm(list=ls())

## Getting the necessary libraries-- 
library(tidyverse)
```


```{r load_data}
## Load in the data we will be using for this assignment: 
load("college.Rdata")
```
## 2.1 - Calculate the average earnings for individuals at the most selective colleges, then compare that with individuals at the least selective colleges in the dataset.

```{r combining commands}
## 2.1 - 
## Calculate the average earnings for very selective schools - top 1%.
sc%>%filter(adm_rate<.1)%>%summarize(mean_earnings=mean(md_earn_wne_p6,na.rm=TRUE))

## And for not very selective schools - greater than top 3%
sc%>%filter(adm_rate>.3)%>%summarize(mean_earnings=mean(md_earn_wne_p6,na.rm=TRUE))


```


## 2.2 - Find a way to determine whether colleges with very high SAT scores tend to be larger or smaller than colleges with low SAT scores.

```{r combining commands 2}

## 2.1 - 
## ## Below is the average mean size (number of undergraduate students) for schools with very high SAT scores (greater than 1250).
sc%>%filter(sat_avg>1250)%>%summarize(mean_size=mean(ugds,na.rm=TRUE))

## Below is the average mean size (number of undergraduate students) for schools with low SAT scores (less than 1000).
sc%>%filter(sat_avg<1000)%>%summarize(mean_size=mean(ugds,na.rm=TRUE))

```


## 2.3 - Plot the relationship between cost and debt. What do you see? Does this surprise you?
## The scatterplot below reveals a positive relationship between cost and debt. As cost rises, debt rises. This does not surprise me. But there is also a lot of debt for $15k - $35k schools which indicates to me these could be forst generation or lower income students accumulating debt.

```{r}

plot(sc$costt4_a, sc$debt_mdn,main="Scatterplot of Cost and Debt", xlab="Cost", ylab="Debt", pch=19)
costdebt<-lm(debt_mdn ~ costt4_a, data = sc)
abline(costdebt)
```


## 2.4 - Now, provide separate plots for cost and debt by control of the institution.
## control: control of institution, 1=public, 2= private non-profit, 3=private for-profit
## The first scatterplot depicts college costs by control of institution.
## The second scatterplot depicts college debt by control of institution.

```{r}
plot(sc$control, sc$costt4_a,main="Scatterplot of Cost and Control", xlab="Control", ylab="Cost", pch=19)
costcontrol <- lm(costt4_a ~ control, data = sc)
abline(costcontrol)


```

```{r}
plot(sc$control, sc$debt_mdn,main="Scatterplot of Debt and Control", xlab="Control", ylab="Debt", pch=19)
debtcontrol<-lm(debt_mdn ~ control, data = sc)
abline(debtcontrol)

```










