---
title: "04-assignment_<crutchfield>.Rmd"
author: "Russell Crutchfield"
date: "9/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 4

```{r}

#library(gdata)  #gdata is finicky ... you may need to install it, but not load it.
library(gdata)
library(tidyverse)
library(haven)
library(readxl)

```



## 1.	Panel data for OECD countries. Save as file name oecd.RData http:
//www.wiley.com/legacy/wileychi/baltagi/supp/Gasoline.dat

```{r}

oecd<-read_table(file="http://www.wiley.com/legacy/wileychi/baltagi/supp/Gasoline.dat")

## Renaming columns:
names(oecd) <- c("Country", "Year", "LGASPCAR", "LINCOMEP", "LRPMG", "LCARPCAP")

head(oecd)

## Save the file: 
##save(oecd,file="oecd.Rdata")

```



## 2.	U.S. National Election Survey data from 2004. Save as file name nes.RData. http://www.uta.edu/faculty/story/DataSets.htm

```{r}

nes<-read_spss("http://www.uta.edu/faculty/story/DataSets/NES2004.sav")

## Removing unwanted columns:
nes <- nes[,-c(3,20,21)]

head(nes)

## Save the file:
##save(nes,file="nes.Rdata")

```



## 3.	General social survey, student version. Save as file name gss.Rdata. http://www.uta.edu/faculty/story/DataSets.htm

```{r}

gss<-read_excel("GeneralSocialSurvey1996ExcelDataStudentVersion.xls",skip=0,col_names = TRUE)


##Removing unwanted columns:
gss <- gss[,-c(10,11)]

head(gss)

## Save the file:
##save(gss,file="gss.Rdata")

```



4.	Replication file for “STATISTICAL DISCRIMINATION OR PREJUDICE? A LARGE SAMPLE FIELD EXPERIMENT”. Open up and save the mainData.csv file. Save it as maindata.RData. Available here, look under the “Data and Analysis” tab.

```{r}

maindata<-read_csv(file = "https://dataverse.harvard.edu/api/access/datafile/:persistentId?persistentId=doi:10.7910/DVN/26410/05NHUX")

##head(csv)

## Save the file:
##save(maindata,file="maindata.Rdata")
```



5. The Lalonde dataset, covering work experiences in the Panel Study of Income Dynamics (psid). Save as psid.RData http://users.nber.org/
~rdehejia/data/psid_controls.txt You’ll find a description of the data
that you’ll need here.

```{r}

psid<-read.table(file="http://users.nber.org/~rdehejia/data/psid_controls.txt")

head(psid)

## rename column names:
names(psid)<-c("treatment",
                "ags",
                "education",
                "Black",
                "Hispanic",
                "married",
                "nondegree",
                "RE74",
                "RE75",
                "RE78")
 

head(psid)

## Save the file:
##save(psid,file="psid.Rdata")

```








