---
title: "07_assignment_crutchfield"
author: "Russell Crutchfield"
date: "9/23/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Assignment 7 (Week 5) - Option 2


```{r scorecard} 
## Clear environment
rm(list=ls())

library(tidyverse)
```

```{r}
### Install the needed packages...
# install.packages("twitteR")
#install.packages("ROAuth")
# install.packages("rtweet")
library(arules)
library(rtweet)
library(twitteR)
library(ROAuth)
library(jsonlite)
library(rjson)
library(tokenizers)
library(tidyverse)
library(tm)
library(wordcloud)
```


## OPTION 2:

## 1. Create a twittR Account. What is your consumerKey? What is your accessToken?
## Apply for a developer account at https://developer.twitter.com/en/apply-for-access . 
## Follow instructions and take note of your API keys and tokens which grant you access.
```{r}

consumerKey='SOxmmtuy4rrTDn5AgGfrEbJCI'
consumerSecret='HKxh1JWHy5lwOYat9nGuP1t9oxUjGBwq6rjFI3yWsYl2czPoRV'
access_Token='714478256418897920-QdraWHbUbkiAkp9sm9ixDpvmSdaAX97'
access_Secret='rLnyySDq4Ak5qNPsjRjURqZDA1YZ1aRD4hN3xhvwgdinL'

requestURL='https://api.twitter.com/oauth/request_token'
accessURL='https://api.twitter.com/oauth/access_token'
authURL='https://api.twitter.com/oauth/authorize'


#filename="TwitterConKey_ConSec_AccTok_AccSec.txt"
#(tokens<-read.csv(filename, header=TRUE, sep=","))
#(consumerKey=as.character(tokens$consumerKey))
#consumerSecret=as.character(tokens$consumerSecret)
#access_Token=as.character(tokens$access_Token)
#access_Secret=as.character(tokens$access_Secret)
```
## 2. Run example 07-twitterAPI.rmd. Use hashtag: Trump. What are the 5 most common words contained within collected tweets?
## Run the following line of code and change the hashtag, n, and date, to what you desire.
## Search<-twitteR::searchTwitter("#Trump",n=10,since="2019-09-18")

```{r}
setup_twitter_oauth(consumerKey,consumerSecret,access_Token,access_Secret)

# Below is the function that scours twitter for a particular hash tag.
# n is the number of tweets to be collected

Search<-twitteR::searchTwitter("#Trump",n=42,since="2019-09-09")
(Search_DF <- twListToDF(Search))

# If you wish to store the tweets in a csv file ... 
TransactionTweetsFile = "tweets.csv"
(Search_DF$text[1])


## Start the file
Trans <- file(TransactionTweetsFile)

## Tokenize tweets into a list of words 
Tokens<-tokenizers::tokenize_words(Search_DF$text[1],stopwords = stopwords::stopwords("en"), 
          lowercase = TRUE,  strip_punct = TRUE, strip_numeric = TRUE,simplify = TRUE)

## Write squished tokens
cat(unlist(str_squish(Tokens)), "\n", file=Trans, sep=",")
close(Trans)

## Add remaining lists of tokens into file
## NOTE - a list of tokens is the set of words from a Tweet

Trans <- file(TransactionTweetsFile, open = "a")
tokenList = Tokens
for(i in 2:nrow(Search_DF)){
  Tokens<-tokenize_words(Search_DF$text[i],stopwords = stopwords::stopwords("en"), 
            lowercase = TRUE,  strip_punct = TRUE, simplify = TRUE)
  cat(unlist(str_squish(Tokens)), "\n", file=Trans, sep=",")
  tokenList <- c(tokenList,  unlist(str_squish(Tokens)))
}
close(Trans)
```

## 3. Run this RMD file and choose your favorite hashtag, e.g. chocolate.Create a wordcloud using words from all collected tweets.

```{r Wordcloud}
## Create a wordcloud, but first transform list of words into a TermDocumentMatrix

cor <- Corpus(VectorSource(tokenList))

tdm <- TermDocumentMatrix(cor)
m <- as.matrix(tdm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

## NOTE:  d contains the words d$word AND frequencies d$freq

wordcloud(d$word,d$freq, colors=c("red","green","blue","orange","black","purple", "seagreen") , random.color = TRUE, min.freq = 2)

```