---
title: "08_09_assignment_crutchfield"
author: "Russell Crutchfield"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(knitr)
library(modelr)
library(caret)
library(forcats)

```

```{r}
# Load Data Sets

test <- read_csv("~/Desktop/Fall 2019/Data Science/scripts/test.csv")
View(test)

training <- read_csv("~/Desktop/Fall 2019/Data Science/scripts/training.csv")
View(training)

```


## Assignment Module 8 + 9
#For this assignment, you’ll be using the lemons dataset, which is a subset of the dataset used for a Kaggle competition described here: https://www.kaggle.com/c/DontGetKicked/data. Your job is to predict which cars are most likely to be lemons.

#Complete the following steps.

## 1. Calculate the proportion of lemons in the training dataset using the IsBadBuy variable.
```{r}
table(training$IsBadBuy)

prop.table(table(training$IsBadBuy))

```

## 2. Calculate the proportion of lemons by Make.
```{r}
table(training$Make)

prop.table(table(training$Make))


```

## 3. Now, predict the probability of being a lemon using a linear model (lm(y~x), with covariates of your choosing from the training dataset.
```{r}
#Using Vehivle Year and Vehicle age as covariables:

lm_mod<-lm(IsBadBuy~
             VehYear+
             VehicleAge,
           data=training,y=TRUE,na.exclude=TRUE);summary(lm_mod)



```

## 4. Make predictions from the linear model.
```{r}
#With these results in hand we can generate predicted probabilities and see if this model did any better. To get predicted probabilities, we need to specify `type=response` in our prediction call. 

training<-training%>%
  mutate(pred_lm=predict(lm_mod,type="response"))
```

```{r}
#We can convert the predictions to a binary variable by setting a "threshold" of .5. Any prediction above .5 is considered to be a 1, anything below, a 0.

training<-training%>%
    mutate(pred_lm_out=ifelse(pred_lm>=.3,1,0))


```

## 5. Now, predict the probability of being a lemon using a logistic regression (glm(y~x,family=binomial(link="logit"))), again using covariates of your choosing.
```{r}
#Using Vehivle Year and Vehicle age as covariables:
logit_mod<-glm(IsBadBuy~
             VehYear+   
             VehicleAge,
             data=training,
            na.action=na.exclude,
            family=binomial(link="logit"),
               y=TRUE)

summary(logit_mod)


```
## 6. Make predictions from the logit model. Make sure these are probabilities. 
```{R}
#With these results in hand we can generate predicted probabilities and see if this model did any better. To get predicted probabilities, we need to specify `type=response` in our prediction call. 

training<-training%>%
  mutate(pred_logit=predict(logit_mod,type="response"))
```

```{r}
#We can convert the predictions to a binary variable by setting a "threshold" of .5. Any prediction above .5 is considered to be a 1, anything below, a 0.

training<-training%>%
    mutate(pred_logit_out=ifelse(pred_logit>=.3,1,0))
```
#for the logit model, I predicted zero and the result was 0 in 63,563 cases.
# For the lm model, I predicted 0 and the result was 0 in 64,007 vases.
# 87% model accuracy.

## 7. Create a confusion matrix from your linear model and your logit model.
```{r}
confusionMatrix(data=as.factor(training$pred_logit_out),reference=as.factor(training$IsBadBuy))

confusionMatrix(data=as.factor(training$pred_lm_out),reference=as.factor(training$IsBadBuy))
```
# 87% model accuracy

## 8. Plot the probability of a car being a bad buy by make.
```{r}
hypo_data<-data_grid(training, VehYear=seq_range(VehYear,n=100), VehicleAge=seq_range(VehicleAge,n=100))%>%  
                     
  mutate(pred=predict(logit_mod,newdata=.,type="response"))
```

And now we're ready to plot. 

```{r}
gg<-ggplot(hypo_data,
           aes(x=VehicleAge,y=pred))
gg<-gg+geom_line()
gg<-gg+xlab("Vehicle Age")+ylab("Predicted Probability Lemons")
gg
```

# The graph shows that as vehicle age increases, the predicted probability of being a lemon increases.

## 9. Create a table that shows the probability of a car being a bad buy by make.
```{r}

lemon_make <-with(training,table(Make,IsBadBuy))

colnames(lemon_make)<-c("Not a Lemon","Lemon")
kable(lemon_make)
lemon_make_prop<-prop.table(lemon_make,margin=1)
kable(lemon_make_prop)

```

##Bonus: Create a heatmap of the probability of a car being a bad buy by make and acquisition type.

```{r}



```

