---
title: "10_assignment_crutchfield"
author: "Russell Crutchfield"
date: "10/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Install Libraries:

library(tidyverse)
library(modelr)
library(caret)
```

```{r}
library(forcats)

```

## Assignment 10

# Based on your previous assignments concerning predictors and classifiers, do the following:

# 1. Create a 10-fold cross validation of your predictor (linear regression) OR classifier (logistic regression, decision tree, or other). Provide a summary table or graphic of the RMSEs OR Accuracies from the cross validation.
```{r}
# Load Data - using ELS data since #2 says "predict reading score..."
load("~/Desktop/Fall 2019/Data Science/scripts/els.Rdata")

```

```{r}
# Using bynels2r, byrace covariables
els<-els%>%
  select(bynels2r,byrace)%>%
  mutate_all(funs(as.numeric))%>%
  tbl_df()


```


```{r}
#Plot
gg<-ggplot(els, aes(x=byrace,y=bynels2r))
gg<-gg+geom_point()
gg

```

```{r}
 ## Define the model
mod1_formula<-formula(bynels2r~byrace)
## Run the model against all of the data
basic.mod<-lm(mod1_formula,
              data=els); summary(basic.mod)


```
# Coefficients are significant
```{r}
# Cross validation tes
els_cf<-els%>%
  crossv_kfold(10)
els_cf


```
```{r}
#Calculate the root mean squared error
rmse_mod1<-els_cf %>% 
  mutate(train = map(train, as_tibble)) %>% ## Convert to tibbles
  mutate(model = map(train, ~ lm(mod1_formula,
                                 data = .))) %>%
  mutate(rmse = map2_dbl(model, test, rmse)) %>% ## apply model, get rmse
  select(.id, rmse) ## pull just id and rmse 

summary(rmse_mod1)
```

```{r}
summary(rmse_mod1$rmse)

#plot
gg<-ggplot(rmse_mod1,aes(rmse))
gg<-gg+geom_density()
gg


```



## 2. Using a random partition, create 100 separate cross validations of your linear model predicting reading scores as a function of at least two covari- ates. Provide a summary table or graphic of the RMSEs from this cross validation.
```{r}

els_cv<-els%>%
crossv_mc(n=100,test=.2) 
els_cv

```

```{r}
mod1_rmse_cv<-els_cv %>% 
  mutate(train = map(train, as_tibble)) %>% ## Convert to tibbles
  mutate(model = map(train, ~ lm(mod1_formula, data = .)))%>%
  mutate(rmse = map2_dbl(model, test, rmse))%>% 
  select(.id, rmse) ## pull just id and rmse 

mod1_rmse_cv

```

```{r}
summary(mod1_rmse_cv$rmse)
```


```{r}

# Plot
gg<-ggplot(mod1_rmse_cv,aes(rmse)) 
gg<-gg+geom_density(bins=50,fill="red",alpha=.2)

gg
```



