---
title: "11_assignment_crutchfield"
author: "Russell Crutchfield"
date: "9/25/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

#Get libraries
library(tidyverse)
library(nycflights13)
library(RSQLite)

```

## Assignment 11 Complete the following steps:

## 1. Using the nyclfights13 library, open all of the data tables and turn them into a database. Make sure to include flights, airlines, airports, weather and planes.
# HINT: Simple – just run the r-chunk from the example, lines 35 – 60.

```{r}

# Data sources from NYC flights
data(flights)
data(airlines)
data(airports)
data(weather)
data(planes)

```

```{r}
con <- dbConnect(RSQLite::SQLite(), ":memory:")

#Write flights tables to database:
dbWriteTable(con,
             "flights", 
             as.data.frame(flights))

dbWriteTable(con,
             "planes", 
             as.data.frame(planes))

dbWriteTable(con,
             "airlines", 
             as.data.frame(airlines))

dbWriteTable(con,
             "weather", 
             as.data.frame(weather))

dbWriteTable(con,
             "airports", 
             as.data.frame(airports))


```


## 2. Create a data frame from a SQL pull from the database that consists only of flights that took off from JFK in May.
# HINT: You will need to send a query to the database. Selecting only flights from ‘JFK’ – don’t forget the quotes!!!
# Try using the following request text: req_text<-"Select * from flights Where origin=='JFK' "
# Then execute the query


```{r}

# select flights, in May, from JFK:
req1_text<-"SELECT * from flights where month = 5 and origin = 'JFK' 
            "
req1<-dbSendQuery(con,req1_text)

req1_df<-dbFetch(req1,n=-1)

dbClearResult(req1)

head(req1_df) 

```


## 3. Create a data frame from a SQL pull from the database that consists only of flights that took off on-time (a delay of less than 10 minutes) from Newark at temperatures of less than 40 degrees F.
# HINT: This request has 3 conditions (from 2 different databases!!) that must be met, thus we will need to connect each condition with an AND ... plus ... we will need to access two databases.
# We will include the join (of both databases) within the request ....
# Try: req_text<-"Select f.dep_delay, f.origin, w.temp 
# FROM flights f
# JOIN weather w
# WHERE f.origin=w.origin AND f.year=w.year AND f.month=w.month AND f.day=w.day AND f.hour=w.hour AND f.origin= <what goes here?> AND f.dep_delay<10 AND w.temp<40"

```{r}
# EWR, Delay less than 10, and temp less than 40

req2_text<-"Select f.dep_delay, f.origin, w.temp 
FROM flights f
JOIN weather w
WHERE f.origin=w.origin AND f.year=w.year AND f.month=w.month AND 
f.day=w.day AND f.hour=w.hour AND f.origin= 'EWR' AND 
f.dep_delay<10 AND w.temp<40
"
req2<-dbSendQuery(con,req2_text)

req2_df<-dbFetch(req2,n=-1)

dbClearResult(req2)

head(req2_df) 

```


## 4. Create data frame from a SQL pull from the database that consists of planes flown by United.
# Hint: since we have already likely created a flights data frame, we can filter all flights flown by United using the “filter(...)” function.

```{r}
# Flights, United

req3_text <- "SELECT * FROM flights WHERE carrier = 'UA'"

req3<-dbSendQuery(con,req3_text)

req3_df<-dbFetch(req3,n=-1)

dbClearResult(req3)

head(req3_df) 

```




