---
title: "12_assignment_crutchfield"
author: "Russell Crutchfield"
date: "10/2/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Assignment 12

##Complete the following steps:

```{r}
# Install Packages:

rm(list = ls())
library(tidyverse)
library(stats)
library(flexclust)
library(ggplot2)
library(LICORS)
library(knitr)
library(modelr)
library(readxl)
```


## 1. Download the student evaluation dataset from the website.
# Hint: You can find this xls file in the repo as well: ev<-read_xlsx("turkiyestudentevaluation_generic.xlsx")

```{r}
# load and view data file:
ev<-read_xlsx("turkiyestudentevaluation_generic.xlsx")
view(ev)
```


## 2. Select a set of 10 related variables that you think might serve as the basis for clustering.
# View the dataframe and identify 10 variables you would like to use for analysis.
# Hint: See syntax in Will’s example on how to select variables, if you forgot ... (or see examples from weeks 1 – 3.)

```{r}
## Selected questions from data dictionary: q2, q8, q9, q11, q13, q14, q16, q18, q22, q24:
ev1 <- ev %>%
  select("Q2", "Q8", "Q9", "Q11", "Q13", "Q14", "Q16", "Q18", "Q22", "Q24")

```


## 3. Run the clustering algorithm kmeanspp to identify 3 clusters. Hint: use kmeanspp ...

```{r}
# Select 3 clusters:
ev_clust <- kmeanspp(ev1, k = 3, start = "random", iter.max = 1000, nstart = 1)
table(ev_clust$cluster)

```


## 4. Summarize the clusters using the variables you selected.
# Analyze your findings ... this will be subjective and up to interpretation. Do you notice any patterns relevant in your clusters??

```{r}
ev1$cluster <- ev_clust$cluster
mycols <- c("Group 1", "Group 2", "Group 3")

#proportions of variables 
pt <- prop.table(table(ev1$cluster, ev1$Q2), margin = 1)

rownames(pt) <- mycols
pt <- pt * 100
pt <- round(pt, 1)
pt

#Group 1 felt objectives were somewhat clear 
#Group 2 felt they weren't clear at all 
#Group 3 felt they were REALLY clear

pt <- prop.table(table(ev1$cluster, ev1$Q8), margin = 1)

rownames(pt) <- mycols
pt <- pt * 100
pt <- round(pt, 1)
pt

#Repeated for the other 8 variables: 
prop.table(table(ev1$cluster, ev1$Q9), margin = 1) %>% kable()
prop.table(table(ev1$cluster, ev1$Q11), margin = 1) %>% kable()
prop.table(table(ev1$cluster, ev1$Q13), margin = 1) %>% kable()
prop.table(table(ev1$cluster, ev1$Q14), margin = 1) %>% kable()
prop.table(table(ev1$cluster, ev1$Q16), margin = 1) %>% kable()
prop.table(table(ev1$cluster, ev1$Q18), margin = 1) %>% kable()
prop.table(table(ev1$cluster, ev1$Q22), margin = 1) %>% kable()
prop.table(table(ev1$cluster, ev1$Q24), margin = 1) %>% kable()

#Summarize variables 
var.means <- colMeans(ev1)
var.means <- var.means[-(length(var.means))]

sum1 <- ev1 %>% group_by(cluster) %>% summarize_all(funs(mean), na.rm = TRUE)
sum1

sum2 <- gather(sum1, -cluster, key = variable, value = value)
sum2
sum_total <- ev1 %>% summarize_all(funs(mean))

sum_total <- gather(sum_total, key = variable, value = overall_mean)
sum2 <- left_join(sum2, sum_total, by = "variable")


sum2 <- sum2 %>% group_by(variable) %>% mutate(varmeans = mean(value))

sum2 <- sum2 %>% group_by(variable) %>% mutate(varmeans = mean(value))

#Variable Names 
variable_labels <- rev(c("Clear Objectives", "Helpful Assessments", "Enjoyed Course", "Relevant for Professional Growth", "Knowledgable Instructor", "Prepared Instructor", "Committed Instructor", "Good Public Speaker", "Open Minded Instructor", "Relevant Assignments-Helpful"))


g1 <- ggplot(data = sum2, aes(y = value, x = variable, fill = variable))
g1 <- g1 + geom_bar(stat = "identity") + coord_flip() + theme(legend.position = "none")
g1 <- g1 + scale_x_discrete(labels = variable_labels)
g1 <- g1 + geom_point(data = sum2, aes(y = overall_mean, x = variable))
g1 <- g1 + facet_wrap(~cluster)
g1


ev1$cluster_name <- NA
ev1$cluster_name[ev1$cluster == 1] <- "Exceedingly Satisfied Students"
ev1$cluster_name[ev1$cluster == 2] <- "Exceedingly Unsatisfied Satisfied Students"
ev1$cluster_name[ev1$cluster == 3] <- "Satisfied Students"
```

## Summary of Cluster Patterns: 
#Cluster 1: Students were exceedingly unsatisfied with the overall Class experience.
#Cluster 2: Students were neutral or satisfied with the overall course experience.
#Cluster 3: Students were exceedingly satidfied with the overall class experience.



## 5. Bonus Question: Try running a HAC algorithm on the data and compare to the results found in #4.

```{r}



```




