---
title: "arm_assignment_crutchfield"
author: "Russell Crutchfield"
date: "10/9/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}

consumerKey='SOxmmtuy4rrTDn5AgGfrEbJCI'
consumerSecret='HKxh1JWHy5lwOYat9nGuP1t9oxUjGBwq6rjFI3yWsYl2czPoRV'
access_Token='714478256418897920-QdraWHbUbkiAkp9sm9ixDpvmSdaAX97'
access_Secret='rLnyySDq4Ak5qNPsjRjURqZDA1YZ1aRD4hN3xhvwgdinL'
```

## Once you have your keys, you can set up the API.

```{r api, include=TRUE}

requestURL='https://api.twitter.com/oauth/request_token'
accessURL='https://api.twitter.com/oauth/access_token'
authURL='https://api.twitter.com/oauth/authorize'



```


```{r}

### Install the needed packages...
#install.packages("twitteR")
#install.packages("ROAuth")
# install.packages("rtweet")
library(arules)
library(rtweet)
library(twitteR)
library(ROAuth)
library(jsonlite)
#install.packages("streamR")
#library(streamR)
#install.packages("rjson")
library(rjson)
#install.packages("tokenizers")
library(tokenizers)
library(tidyverse)
library(plyr)
library(dplyr)
library(ggplot2)
#install.packages("syuzhet")  ## sentiment analysis
library(syuzhet)
library(stringr)
#install.packages("arulesViz")
library(arulesViz)
library(tm)
library(wordcloud)
```

## 1. Run the ARM coded example provided and choose a hashtag of your liking and collect 100 tweets. What hashtag did you choose?

```{r}

## Using #Vaping
setup_twitter_oauth(consumerKey,consumerSecret,access_Token,access_Secret)

Search<-twitteR::searchTwitter("#Vaping",n=100,since="2018-09-09")
(Search_DF <- twListToDF(Search))
TransactionTweetsFile = "Choc.csv"
(Search_DF$text[1])

## Start the file
Trans <- file(TransactionTweetsFile)
## Tokenize to words 
Tokens<-tokenizers::tokenize_words(Search_DF$text[1],stopwords = stopwords::stopwords("en"), 
          lowercase = TRUE,  strip_punct = TRUE, strip_numeric = TRUE,simplify = TRUE)
## Write squished tokens
cat(unlist(str_squish(Tokens)), "\n", file=Trans, sep=",")
close(Trans)
## Append remaining lists of tokens into file
## Recall - a list of tokens is the set of words from a Tweet
Trans <- file(TransactionTweetsFile, open = "a")
tokenList = Tokens #add this line!!
for(i in 2:nrow(Search_DF)){
  Tokens<-tokenize_words(Search_DF$text[i],stopwords = stopwords::stopwords("en"), 
            lowercase = TRUE,  strip_punct = TRUE, simplify = TRUE)
  cat(unlist(str_squish(Tokens)), "\n", file=Trans, sep=",")
  tokenList <- c(tokenList, unlist(str_squish(Tokens))) #Add this line!!
}
close(Trans)
```


## 2. Create a wordcloud of all words from all tweets collected, and identify words that are non- informative and should be removed for the purposes of analysis (stopwords). What stopwords did you choose.

```{r}

cor <- Corpus(VectorSource(tokenList))

tdm <- TermDocumentMatrix(cor)
m <- as.matrix(tdm)
v <- sort(rowSums(m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)
## NOTE: d contains the words d$word AND frequencies d$freq
wordcloud(d$word,d$freq, colors=c("red","green","blue","orange","black","purple", "seagreen") , random.color = TRUE, min.freq = 3)

```


## 3. Create transaction data from the tweets and identify 5 rules that are “most interesting”. What criteria did you use to determine whether a rule was “interesting”? Hint: Lift, Support, Confidence, ... ?

```{r}
detach(package:tm, unload=TRUE)
######### Read in the tweet transactions
TweetTrans <- read.transactions(TransactionTweetsFile,
                                rm.duplicates = FALSE, 
                                format = "basket",
                                sep=","
                                ## cols = 
                                )
inspect(TweetTrans)
## See the words that occur the most
Sample_Trans <- sample(TweetTrans, 50)
summary(Sample_Trans)
## Read the transactions data into a dataframe
TweetDF <- read.csv(TransactionTweetsFile, header = FALSE, sep = ",")
head(TweetDF)
(str(TweetDF))


## Convert all columns to char 
TweetDF<-TweetDF %>%
  mutate_all(as.character)
(str(TweetDF))
# We can now remove certain words
TweetDF[TweetDF == "t.co"] <- ""
TweetDF[TweetDF == "rt"] <- ""
TweetDF[TweetDF == "http"] <- ""
TweetDF[TweetDF == "https"] <- ""
## Clean with grepl - every row in each column
MyDF<-NULL
for (i in 1:ncol(TweetDF)){
  MyList=c() # each list is a column of logicals ...
  MyList=c(MyList,grepl("[[:digit:]]", TweetDF[[i]]))
  MyDF<-cbind(MyDF,MyList)  ## create a logical DF
  ## TRUE is when a cell has a word that contains digits
}
## For all TRUE, replace with blank
TweetDF[MyDF] <- ""
(head(TweetDF,10))
# Now we save the dataframe using the write table command 
write.table(TweetDF, file = "UpdatedChocolate.csv", col.names = FALSE, 
            row.names = FALSE, sep = ",")
TweetTrans <- read.transactions("UpdatedChocolate.csv", sep =",", 
            format("basket"),  rm.duplicates = TRUE)
inspect(TweetTrans)


# So that you do not have an enormous amount of rules, you can thresholds for
# support, confidence and lift ... also minlength for the rules. 
TweetTrans_rules = arules::apriori(TweetTrans, 
            parameter = list(support=.025, confidence=.75, minlen=3))
inspect(TweetTrans_rules[1:10])
## sorted
SortedRules_conf <- sort(TweetTrans_rules, by="confidence", decreasing=TRUE)
inspect(SortedRules_conf[1:20])
SortedRules_sup <- sort(TweetTrans_rules, by="support", decreasing=TRUE)
inspect(SortedRules_sup[1:20])

```


```


## 4. Create a visualization (using arulesviz or another) of the rules found as a result of your ARM model.

```{r}

plot (SortedRules_sup[1:50],method="graph",interactive=TRUE,shading="confidence") 
plot (SortedRules_conf[1:50],method="graph",interactive=TRUE,shading="confidence") 


```














